Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-23 main.tex
:pencil: Rephrase passive beamforming

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform, active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner. Numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

@@

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{\text{I,}n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\text{I,}n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\text{I,}n,m}\tilde{x}_{\text{I,}n}(t)}+w_{\text{P,}n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$. Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq \boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t)$, where
			\begin{align}
				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{h}_{\text{R,}n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\text{I,}n} = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\text{R,}n}^H)\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment. For each IRS element, the reflection coefficient is shared by $M$ AP-IRS-user channels over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\text{I}}(t)+y_\text{P}(t)$ captures the contribution from information and power components over all subbands, where
			\begin{align}
				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\,,\label{eq:y_I}\\
				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\,.\label{eq:y_P}
			\end{align}
		\end{subsection}

@@

			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i\,.

@@

			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}\,.

@@

			\begin{figure*}[b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)\,.\label{eq:z_expand}
				\end{equation}
				\hrule
				\begin{flalign}
					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h}\,,&&\label{eq:y_I2}\\
					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2\,,&&\label{eq:y_I4}
				\end{flalign}
				\begin{align}
					\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h}\,,\label{eq:y_P2}\\
					\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H\,.\label{eq:y_P4}
				\end{align}
			\end{figure*}
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1\,.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate as the variables are coupled and the objective function \eqref{ob:original}, the rate constraint \eqref{co:original_rate}, and the IRS magnitude constraint \eqref{co:original_modulus} are non-convex. To achieve a feasible solution, we propose an AO algorithm that iteratively updates the waveform and active beamforming at the transmitter, the phase shifts at the IRS, and the power splitting ratio at the receiver, until convergence.
		\begin{remark}\label{re:irs_subchannel_alignment}
			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		\end{remark}

@@

			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n=[\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}}=[\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi}=\bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n = \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{\text{I/P,}k}$ as

@@

				& = \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\

@@

			where $\boldsymbol{V}=[\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M}=[\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k}=\boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, we rewrite the rate and objective expressions as

@@

				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)}\,,\label{eq:R_irs}\\

@@

				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}\,.\label{eq:z_irs}

@@

			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are

@@

				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2\,,\label{eq:taylor_1}\\

@@

				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*\,,\label{eq:taylor_2}\\

@@

			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}. Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to

@@

					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 (t_{\text{I,}0}^{(i)})(t_{\text{I,}0}^{(i-1)}) - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right)\,.\label{eq:z_irs_approx}

@@

				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\,.\label{co:irs_rank}}

@@

				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}\,.

@@

				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right)\,.

@@

					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right)\,.\label{eq:z_waveform}

@@

				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}\,.}

@@

				\addConstraint{\rho + \bar{\rho} \le 1\,.}

>>>>

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization by Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs a low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in an efficient and reliable manner. Numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

@@

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{\text{I,}n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{\text{I,}n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{\text{I,}n,m}\tilde{x}_{\text{I,}n}(t)}+w_{\text{P,}n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{\text{I/P,}n,m}$ denotes the weight of the information/power signal transmitted by antenna $m$ at subband $n$. Stacking up the entries on all transmit antennas, we further define $\boldsymbol{w}_{\text{I/P,}n} \triangleq [w_{\text{I/P,}n,1},\dots,w_{\text{I/P,}n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t) \triangleq \boldsymbol{x}_{\text{I}}(t)+\boldsymbol{x}_{\text{P}}(t)$, where
			\begin{align}
				\boldsymbol{x}_{\text{I}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t){e^{j2{\pi}{f_n}{t}}}\right\}},\label{eq:x_I}\\
				\boldsymbol{x}_{\text{P}}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}}.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, we denote the AP-user direct channel as $\boldsymbol{h}_{\text{D,}n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{\text{R,}n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l \triangleq \alpha_l e^{j\theta_l}$ with the reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Also, define the IRS matrix as $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The auxiliary link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided auxiliary channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{h}_{\text{R,}n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\text{I,}n} = \boldsymbol{h}_{\text{D,}n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\text{R,}n}^H)\boldsymbol{H}_{\text{I,}n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}\label{re:irs_frequency_flat}
				Due to hardware constraints, independent phase shift control for different frequencies is prohibited and the IRS is frequency-flat. Hence, the auxiliary channels at different frequencies cannot be simultaneously maximized and there is a tradeoff in subchannel alignment. For each IRS element, the reflection coefficient is shared by $M$ AP-IRS-user channels over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Receive Signal}
			At the single-antenna receiver, the total received signal $y(t) \triangleq y_{\text{I}}(t)+y_\text{P}(t)$ captures the contribution from information and power components over all subbands, where
			\begin{align}
				y_{\text{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\text{I,}n}\tilde{x}_{\text{I,}n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
				y_{\text{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\text{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}.\label{eq:y_P}
			\end{align}
		\end{subsection}

@@

			% 	i_{\text{D}}(t)=\sum_{i=0}^{\infty}k_i'\rho^{i/2}R_{\text{ant}}^{i/2}y(t)^i.

@@

			% 	i_{\text{out}}(t)=\mathcal{A}\{i_{\text{D}}(t)\}\approx\sum_{i=0}^{n_0}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y(t)^i\right\}}\right\}.

@@

			\begin{figure*}[b]
				\hrule
				\begin{equation}
					z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho) = \beta_2\rho\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}\Bigr).\label{eq:z_expand}
				\end{equation}
				\hrule
				\begin{flalign}
					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^2(t)\right\}\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h},&&\label{eq:y_I2}\\
					\mathcal{E}\left\{\mathcal{A}\left\{y_{\text{I}}^4(t)\right\}\right\}
					& = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{I,}n})^H}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\text{I,}0}\boldsymbol{h})^2,&&\label{eq:y_I4}
				\end{flalign}
				\begin{flalign}
					\mathcal{A}\left\{y_{\text{P}}^2(t)\right\}
					& = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\text{P},n})^H} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}0}\boldsymbol{h},&&\label{eq:y_P2}\\
					\mathcal{A}\left\{y_{\text{P}}^4(t)\right\}
					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\text{P,}{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\text{P,}{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\text{P,}{n_3}})^H(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\text{P,}{n_4}})^H} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\text{P,}k}\boldsymbol{h})^H.&&\label{eq:y_P4}
				\end{flalign}
			\end{figure*}
		\end{subsection}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize the R-E region through a current maximization problem subject to transmit power, IRS magnitude, and rate constraints
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\boldsymbol{w}_\text{P},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\text{I}}}\rVert^2+\lVert{\boldsymbol{w}_\text{P}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\text{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}
		Problem~\eqref{op:original} is intricate with coupled variables in non-convex expressions \eqref{ob:original}, \eqref{co:original_rate}, \eqref{co:original_modulus}. To obtain a feasible solution, we propose an AO algorithm that iteratively updates 1) the phase shift at the IRS, 2) the waveform, active beamforming at the transmitter and the power splitting ratio at the receiver, until convergence.
		\begin{remark}\label{re:irs_subchannel_alignment}
			As information and power transfer prefer different subchannel strength distribution, the frequency-flat characteristic of the IRS introduces a resource allocation problem. Following Remark \ref{re:irs_frequency_flat}, if the IRS is frequency-selective and there is only one transmit antenna, then each reflector can simultaneously align the corresponding AP-IRS-user channel with the AP-user channel at all subbands. In this case, the strengths of all subchannels are maximized so that the joint design would follow straightforwardly from existing SWIPT work \cite{Clerckx2018b}.
		\end{remark}

@@

			where $t$ is an auxiliary variable with unit modulus, $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\text{D,}n}]^H \in \mathbb{C}^{(L+1) \times M}$, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t]^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\text{I,}n}\boldsymbol{w}_{\text{I,}n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$. On the other hand, we define $t_{\text{I/P,}k}$ as

@@

				& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{h}\nonumber\\

@@

			where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\text{I/P,}k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\text{I/P,}k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$. Therefore, we rewrite the rate and objective expressions as

@@

				& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{Tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\

@@

				& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\text{I,}0}t_{\text{P,}0}.\label{eq:z_irs}

@@

			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by their first-order Taylor expansion \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are

@@

				& \ge 2 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - (t_{\text{I,}0}^{(i-1)})^2,\label{eq:taylor_1}\\

@@

				& \ge 2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*,\label{eq:taylor_2}\\

@@

			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}. Hence, the objective function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to

@@

					& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\text{I,}0}^{(i)}t_{\text{I,}0}^{(i-1)} - 2 (t_{\text{I,}0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\text{P,}k}^{(i)} (t_{\text{P,}k}^{(i-1)})^*\right\} - t_{\text{P,}k}^{(i-1)} (t_{\text{P,}k}^{(i-1)})^*}\right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\text{I,}0}^{(i)} + t_{\text{P,}0}^{(i)})(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)}) - \frac{1}{4}(t_{\text{I,}0}^{(i-1)} + t_{\text{P,}0}^{(i-1)})^2 - \frac{1}{4}(t_{\text{I,}0}^{(i)} - t_{\text{P,}0}^{(i)})^2\right).\label{eq:z_irs_approx}

@@

				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}

@@

				\boldsymbol{w}_{\text{I/P,}n}=s_{\text{I/P,}n}\frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.

@@

				R(\boldsymbol{s}_{\text{I}},\rho) = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\text{I,}n}^2}{\sigma_n^2}\biggr)\right).

@@

					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\text{I,}{n_1}}^2 s_{\text{P,}{n_2}}^2 \right).\label{eq:z_waveform}

@@

				\addConstraint{R(\boldsymbol{s}_{\text{I}},\rho) \ge \bar{R}.}

@@

				\addConstraint{\rho + \bar{\rho} \le 1.}
